---
title: "Reproducible Document"
author: "Anders Hammer Nielsen-Kudsk"
format: html
---
    
```{r setup}
#| message: false
#| warning: false
library(tidyverse)

post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))

small_post_meal_data <- select(post_meal_data, id, Age, BMI, Group, auc_pg, auc_ins, glykemi)
```

## About me
- Anders Hammer Nielsen-Kudsk
- Steno Diabetes Center Aarhus
- Institut for Klinisk Medicin, Aarhus Universitet

I am a PhD student at **Steno** *Diabetes* Center Aarhus. I was enrolled 1 December 2025.

## Testing for Git
The sun is hitting my face and there are no curtains

## Simple code
```{r}
3 * 3
```


## Writing R code

```{r}
2 + 2
```

## Showing the data
```{r}
post_meal_data

glimpse(post_meal_data)
```

## Plot one continuous variable
```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

See @fig-bmi-histo


## Exercise: discrete plots
```{r}
#| fig-cap: "Visualizing glykemi"
#| label: fig-glykemi-bar
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

See @fig-glykemi-bar above for a cool plot!

## Plotting two discrete variables

```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Side by side plots

```{r fig-bmi-glycemia}
#| fig-cap: "BMI and glycemia, side by side"
#| fig-subcap:
#|  - "Distribution of BMI."
#|  - "Number of those with glycemia"
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```


## Plotting two continuous variables
```{r}
#| fig-cap: "Scatterplot of BMI and the area under the curve for glucose"
#| label: fig-bmi-auc-pg
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```


## Selecting data
```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Group)

select(post_meal_data, starts_with("PG"))

select(post_meal_data, ends_with("DXA"))

select(post_meal_data, contains("0"))
```


## Renaming Columns
```{r}
small_post_meal_data %>%
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  )
```
